### 2025-05-06 Chapters/paper3.tex
Updated paper3 and compiled files

\begin{figure}[htbp]
	\centering
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/loss plot}
		\caption{Loss plot}
		\label{fig:loss-plot}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/accuracy plot}
		\caption{Accuracy plot}
		\label{fig:accuracy-plot}
	\end{minipage}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/transformer_encoder_on²}
		\caption{Transformer Encoder Complexity}
		\label{fig:transformerencoderon2}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/data_loading_complexity_with_legend_updated}
		\caption{Data Loading Complexity}
		\label{fig:dataloadingcomplexitywithlegendupdated}
	\end{minipage}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/evaluation_oe_val·…}
		\caption{Evaluation Complexity}
		\label{fig:evaluationoeval}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/fully_connected_layer_o1}
		\caption{Fully Connected Layer Complexity}
		\label{fig:fullyconnectedlayero1}
	\end{minipage}
\end{figure}

\begin{figure}[htbp]
	\centering
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/gcn_layers_on}
		\caption{GCN Layers Complexity}
		\label{fig:gcnlayerson}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/training_loop_ot·…}
		\caption{Training Loop Complexity}
		\label{fig:trainingloopot}
	\end{minipage}
\end{figure}

>>>>

\begin{center}
	\begin{minipage}[t]{0.48\textwidth}
		\begin{align}
			\text{Accuracy} &= \frac{TP + TN}{TP + TN + FP + FN} \\
			\text{Precision} &= \frac{TP}{TP + FP} \\
			\text{Recall} &= \frac{TP}{TP + FN} \\
			\text{F1\text{-}Score} &= 2 \cdot \frac{\text{Precision} \cdot \text{Recall}}{\text{Precision} + \text{Recall}} \\
			\text{Support} &= TP + FN \\
			\text{Specificity} &= \frac{TN}{TN + FP}
		\end{align}
	\end{minipage}
	\hfill	
	\begin{minipage}[t]{0.48\textwidth}
		\begin{align}
			\text{Macro Precision} &= \frac{1}{C} \sum_{i=1}^{C} \frac{TP_i}{TP_i + FP_i} \\
			\text{Weighted Precision} &= \sum_{i=1}^{C} \frac{n_i}{N} \cdot \frac{TP_i}{TP_i + FP_i} \\
			\mathcal{L}_{CE} &= -\sum_{i=1}^{C} y_i \log(\hat{y}_i) \\
			\mathcal{L}_{FL} &= -\alpha_t (1 - p_t)^\gamma \log(p_t)
		\end{align}
	\end{minipage}
\end{center}
\begin{figure}[htbp]
	\centering
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/loss plot}
		\caption{Loss plot}
		\label{fig:loss-plot}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{img/paper_3/accuracy plot}
		\caption{Accuracy plot}
		\label{fig:accuracy-plot}
	\end{minipage}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{minipage}[b]{0.40\linewidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_3/preprocessing_on³}
		\caption{Preprocessing (\(O(MN^3 + KEN + MN)\))}
		\label{fig:preprocessingon3}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.40\linewidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_3/training_loop_ot·…}
		\caption{Training Loop (\(O(T(LN + 2N^2D/10^4 + DC))\))}
		\label{fig:trainingloopot}
	\end{minipage}
\end{figure}

\noindent Preprocessing: \(O(MN^3 + KEN + MN)\) \\
Training Loop: \(O(T(LN + 2N^2D/10^4 + DC))\)

\begin{figure}[H]
	\centering
	\begin{minipage}[b]{0.40\linewidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_3/gcn_layers_on}
		\caption{GCN Layers (\(O(LN)\))}
		\label{fig:gcnlayerson}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.40\linewidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_3/transformer_encoder_on²}
		\caption{Transformer Encoder (\(O(N^2D)\))}
		\label{fig:transformerencoderon2}
	\end{minipage}
\end{figure}

\noindent GCN Layers: \(O(LN)\) \\
Transformer Encoder: \(O(N^2D)\)

\begin{figure}[H]
	\centering
	\begin{minipage}[b]{0.40\linewidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_3/evaluation_oe_val·…}
		\caption{Evaluation Loop (\(O(E_{\text{val}}(LN + 2N^2D/10^4 + DC))\))}
		\label{fig:evaluationoeval}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.40\linewidth}
		\centering
		\includegraphics[width=\linewidth]{img/paper_3/fully_connected_layer_o1}
		\caption{Fully Connected Layer (\(O(DC)\))}
		\label{fig:fullyconnectedlayero1}
	\end{minipage}
\end{figure}

\noindent Evaluation Loop: \(O(E_{\text{val}}(LN + 2N^2D/10^4 + DC))\) \\
Fully Connected Layer: \(O(DC)\)
